On the Construction of a Collision-Free Schedule of Beacons in a Wireless Multi-Hop Network

### 2013-10-07 paper.tex
added example

>>>>

\subsection{An Example}
An example of medium access is presented in Fig.~\ref{fig:medium-access}.
It shows the access to the medium from the point of view of station A.
After transmitting its beacon, station A is free to transmit and request packets from and to its neighbours.
In this particular example A transmits a packet to A and then a packet to B.
Then, it uses its remaining time to request and receive two packets from A.
The two packets are requested in the poll message.

The next beacon spot is free from A's point of view.
Therefore A can contend for the medium using CSMA/CA and in this transmission it is exposed to the hidden terminal interference.

Even though it is not shown in the figure, at a later time B transmits its beacon. 
Then A has to remain silent unless B explicitly requests a packet from A using a poll.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/medium-access}
  \caption{Medium Access}
  \label{fig:medium-access}
\end{figure}
